Analysis of transit delays in the Toronto Transit Commission: 2024

### 2024-09-26 paper/paper.qmd
Update paper.qmd

>>>>

Figure 3:The trend of delays based on the day of the week

Figure 3 shows the trend of delays based on the day of the week. We can observe which day experiences the most delays and which day experiences the least. It also provides an overview of the delay trend throughout the week.

This information offers valuable insight for the TTC to prepare alternative solutions for delays. For instance, they could deploy more buses or trains on days with higher delays compared to days with fewer delays.
